Treatment planning for HDR Brachytherapy

### 2015-03-28 Paper Seminar/classification.tex
Fixed file

A wonderful classification. To be edited. Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!Make it seen!

>>>>

While using computer aided systems to create treatment plans, this involves time-consuming calculations during optimizations (as seen in this project). Therefore, a classification attempt is proposed, using prior knowledge to reduce the amount of time taken to process.

\subsection{General Idea}
When classifying, you search for similarities or analogies in your given set of data. These provide a basis for a comparison among previously created optimiziations
